---
title: "Temperaturesensor"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
# This project is analyzing humidity levels with a sensor probe on a raspberry pi. 
# Austin and I are writing a program to meausre the humidity levels. 
# The goal is to write a sufficent program that can analzye the data the probe is going to read. 
# The sensor probe has been ordered. I have downloaded the programs onto the raspberry pi that are needed for the sensor. 
# Installed the newest version of Raspbian to communicate with the probe. 
# It is a one wire temperature sensor. 







#Importing The .csv File
temp <- read.csv("TemperatureHourData.csv", header = TRUE, sep = ",")
curve
#Plotting The Temperature Data
```{r}
plot(temp$Temperature ~ temp$Hour, xlab="Time (Hours)", ylab="Temperature (F)", main="Temperature Over 24 Hours") 
curve(predict(model,newdata = list(Hour=x)), add=TRUE)
```
#NLS
```{r}
model <- nls(Temperature~a*(sin(b*Hour+c))+d, data=temp, start=list(a=1, b=pi/12, c=0, d=72.5))
```

